---
title: "Words of a Feather Flock Together- Data Analysis"
author: "Katarina Stekic"
date: "May, 2021"
output:   
  html_document:
    keep_md: true
    theme: journal
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: false
    code_folding: hide
---


#### Loading Libaries
```{r Loading Libraries, include = FALSE}
library(tidyverse)
library(ggthemes)
library(plyr)
library(lme4)
library(afex)
library(emmeans)
library(kableExtra)
library(binom)
library(Rmisc)
library(magick)
library(webshot)
library(magrittr)
library(multcomp)
library(BSDA)
```

```{r Loading GGTheme, include = FALSE}
theme_alan <- function(base_size = 12 , base_family = "")
{
  half_line <- base_size/2
  colors <- ggthemes_data$few
  gray <- colors$medium["gray"]
  black <- colors$dark["black"]
  
  theme(
    line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"),
    rect = element_rect(fill = "white", 
                        colour = "black", size = 0.5, linetype = 1),
    text = element_text(family = base_family, face = "plain", colour = "black", 
                        size = base_size, lineheight = 0.9, hjust = 0.5, vjust = 0.5,
                        angle = 0, margin = margin(), debug = FALSE),
    
    axis.line = element_blank(),
    axis.line.x = NULL,
    axis.line.y = NULL, 
    axis.text = element_text(size = rel(0.8), colour = "grey30"),
    axis.text.x = element_text(margin = margin(t = 0.8 * half_line/2), vjust = 1),
    axis.text.x.top = element_text(margin = margin(b = 0.8 * half_line/2), vjust = 0),
    axis.text.y = element_text(margin = margin(r = 0.8 * half_line/2), hjust = 1),
    axis.text.y.right = element_text(margin = margin(l = 0.8 * half_line/2), hjust = 0), 
    axis.ticks = element_line(colour = "grey20"), 
    axis.ticks.length = unit(half_line/2, "pt"),
    axis.title.x = element_text(margin = margin(t = half_line), vjust = 1),
    axis.title.x.top = element_text(margin = margin(b = half_line), vjust = 0),
    axis.title.y = element_text(angle = 90, margin = margin(r = half_line), vjust = 1),
    axis.title.y.right = element_text(angle = -90, margin = margin(l = half_line), vjust = 0),
    
    legend.background = element_rect(colour = NA),
    legend.spacing = unit(0.4, "cm"), 
    legend.spacing.x = NULL, 
    legend.spacing.y = NULL,
    legend.margin = margin(0.2, 0.2, 0.2, 0.2, "cm"),
    legend.key = element_rect(fill = "white", colour = NA), 
    legend.key.size = unit(1.2, "lines"), 
    legend.key.height = NULL,
    legend.key.width = NULL,
    legend.text = element_text(size = rel(0.8)), 
    legend.text.align = NULL,
    legend.title = element_text(hjust = 0),
    legend.title.align = NULL,
    legend.position = "right", 
    legend.direction = NULL,
    legend.justification = "center", 
    legend.box = NULL,
    legend.box.margin = margin(0, 0, 0, 0, "cm"),
    legend.box.background = element_blank(),
    legend.box.spacing = unit(0.4, "cm"),
    
    panel.background = element_rect(fill = "white", colour = NA),
    panel.border = element_rect(fill = NA, colour = "grey20"),
    panel.grid.major = element_line(colour = "grey92"),
    panel.grid.minor = element_line(colour = "grey92", size = 0.25),
    panel.spacing = unit(half_line, "pt"),
    panel.spacing.x = NULL,
    panel.spacing.y = NULL,
    panel.ontop = FALSE,
    
    strip.background = element_rect(fill = "NA", colour = "NA"),
    strip.text = element_text(colour = "grey10", size = rel(0.8)),
    strip.text.x = element_text(margin = margin(t = half_line, b = half_line)),
    strip.text.y = element_text(angle = 0, margin = margin(l = half_line, r = half_line)),
    strip.placement = "inside",
    strip.placement.x = NULL, 
    strip.placement.y = NULL,
    strip.switch.pad.grid = unit(0.1, "cm"), 
    strip.switch.pad.wrap = unit(0.1, "cm"), 
    
    plot.background = element_rect(colour = "white"),
    plot.title = element_text(size = rel(1.2), hjust = 0, vjust = 1, margin = margin(b = half_line * 1.2)),
    plot.subtitle = element_text(size = rel(0.9), hjust = 0, vjust = 1, margin = margin(b = half_line * 0.9)),
    plot.caption = element_text(size = rel(0.9), hjust = 1, vjust = 1, margin = margin(t = half_line * 0.9)), 
    plot.margin = margin(half_line, half_line, half_line, half_line),
    
    complete = TRUE)
}
pd <- position_dodge(width = 0.1)
```

```{r Centering Function, include = FALSE}
#Just a piece of code that will center a numeric factor on zero
center_scale <- function(x) {
    scale(x, scale = FALSE)
}
```

####Loading Data
```{r Loading Data, message = FALSE, warning = FALSE}

# Our data is in two formats because of a change in jsPsych version halfway through our data collection - thus we read those separate data file types (distinguishable by file size) in here separately, then combine them into a single large data frame

setwd("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/50s/")
files50  <- list.files(pattern = '\\.csv')
tables50 <- lapply(files50, read.csv, header = TRUE)
combined.df.50 <- do.call(rbind , tables50)

combined.df.50[] <- lapply(combined.df.50, function(x) gsub("\\\\", "", x))

setwd("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/40s/")
files40  <- list.files(pattern = '\\.csv')
tables40 <- lapply(files40, read.csv, header = TRUE)
combined.df.40 <- do.call(rbind , tables40)

colnames(combined.df.50)<- c("rtD", "key_press", "trialtype2", "TrialIndex", "elapsed", "node_id", "viewhist", "responses", "Yoking", "RT", "RespKey", "RespCorr", "TrialType", "Image", "Label", "Location", "CorrectResponse", "Block", "BlockTrial", "Condition", "LabelType", "Subcondition", "TrialNum")


colnames(combined.df.40)<- c("rtD", "key_press", "trialtype2", "TrialIndex", "elapsed", "node_id", "viewhist", "responses", "Yoking", "RT", "RespKey", "RespCorr", "TrialType", "Image", "Label", "Location", "CorrectResponse", "Block", "BlockTrial", "Condition", "LabelType", "Subcondition", "TrialNum")
  
combined.df <- rbind(combined.df.50, combined.df.40)

```

## Cleaning Up the Data
```{r Data Cleaning, warning = FALSE}
#1- Substitute out some special characters
combined.df[] <- lapply(combined.df, function(x) gsub("\\\\", "", x))
combined.df[] <- lapply(combined.df, function(x) gsub("[{}]", "", x))
combined.df[] <- lapply(combined.df, function(x) gsub("\"", "", x))

#2- Add in a column with the biographical data (which is currently stored in a single value on the fourth line of each participant's file)
biodata <- combined.df[seq(4, nrow(combined.df), 246),]
biodata <- as.data.frame(biodata$responses)
colnames(biodata) <- "biodata"

biodata <- separate(biodata, col=biodata, into = c("Age", "Gender", "Specify"), sep = ",")

biodata$Age <- sub("age:", "", biodata$Age)
biodata$Gender <- sub("gender:", "", biodata$Gender)
biodata$Specify <- sub("specify:", "", biodata$Specify)

combined.df$Age <- rep(biodata$Age, each = 246)
combined.df$Gender <- rep(biodata$Gender, each = 246)

#3- Add a unique participantID (actually the name of each file)
files <- c(files40, files50)
files <- sub(".csv", "", files)

combined.df$ParticipantID <- rep(files, each= 246)

```

####Cleaning up the Data 2
```{r Cleaning up the Data 2}

#4- Clean up our Data, Get rid of some useless columns, and re-sort the remaining columns into ones we will actually use
CleanData <- subset(combined.df, select = c("ParticipantID", "Condition", "Subcondition", "Yoking", "TrialNum", "TrialType", "Block", "BlockTrial", "Image", "Label", "Location", "CorrectResponse", "RespKey", "RespCorr", "RT"))

#5- Get rid of extra lines from the jsPsych output- leaving us with only our Trial data (everything else of use we've extracted and added as columns)
CleanData <- subset(CleanData, TrialNum > 0)

#6- Set the data types of our various columns
CleanData$ParticipantID <- as.factor(CleanData$ParticipantID)
CleanData$Condition <- as.factor(CleanData$Condition)
CleanData$Subcondition <- as.factor(CleanData$Subcondition)
CleanData$Yoking <- as.factor(CleanData$Yoking)
CleanData$TrialType <- as.factor(CleanData$TrialType)
CleanData$Location <- as.factor(CleanData$Location)

CleanData$TrialNum <- as.numeric(CleanData$TrialNum)
CleanData$Block <- as.numeric(CleanData$Block)
CleanData$BlockTrial <- as.numeric(CleanData$BlockTrial)
CleanData$RespCorr <- as.numeric(CleanData$RespCorr)
CleanData$RT <- as.numeric(CleanData$RT)

write.csv(CleanData, file=("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanData.csv"))
```

We have all of our data combined, but it has to be cleaned up considerably (tidied)

1) remove all of the slashes and backslashes everywhere to have data that we can actually read and parse properly with later commands
2) Extract the biological data from the participants, which is on line 4 of each participant's dataframe, then put it back into the main dataframe as the Age and Gender columns
3) Add a unique participantID column (from the filenames)
4) Trim down to the required columns and re-order them
5) Delete the useless rows
6) Make sure the columns are all the right data types

The basics of tidying are now done, but we should take a visual look at the data- for example looking for impossible values

1) By sorting the "RespCorr" (Correctness of response where 0 = Incorrect and 1 = Correct) it can be noted that we have a single case where the value is "NA"- this is Testing Trial 1 for the participant 7gtriiTixvBaQ . Because we can't be certain what went wrong here, and whether the other data obtained from the participant is of good quality (visually it appears to be fairly good, with the participants fairly uniformly taking about 5 seconds per trial and being correct on about half of trials), the most conservative approach is the simply throw out all of the data from this participant, in case something larger went wrong.

2) Sorting the RT (response time) column reveals a number of strange values:
    
    a) First, there are a number of **negative** RT values, which are actually impossible
      -These are from two participants- there are 17 from participant 60CBPiTiO1gKw and 1 from participant k3LHwiTiOx7fx. As above, we will simply remove          these participants from our data entirely
      
    b) Second, there are some very **high** RT values, with the highest being `r max(CleanData.RTNegCorr$RT)/1000` seconds (`r       max(CleanData.RTNegCorr$RT)/1000/60` minutes or `r max(CleanData.RTNegCorr$RT)/1000/60/60` hours). This is patently too long for a single trial - beyond the realm where we might consider that a participant could be simply evaluating possible correct responses- This long of a break also almost certainly has negative learning consequences. As such, we must set a baseline for removing participants who have individual trials over a certain length. Here we will use 2 minutes (`r 2*60*1000` milliseconds) as a cutoff time to eliminate **all** trials for a participant. Note that we remove individual trials with lengths over 30 seconds in a section below- those we view as outliers for participants responding normally, whereas trials over 2 minutes in length suggest a failure of attention and/or multitasking that could deleteriously effect the results on **all** trials.
    
    The prospect of divided attention is broadly supported by looking at these trials- we can see that the `r nrow(RTHigh)` trials with RTs over 2 minutes are from `r length(unique(RTHigh$ParticipantID))` participants. 
    
 # Data Exclusion

We need to explore what data will be excluded from any further analysis off the top
Roughly we are looking for any irregularities in Reaction Time or other response data that we think would unduly affect our data

We remove data from participants for the following reasons:

A) `r nrow(CleanData[is.na(CleanData$RespCorr),])` participant (ID # `r CleanData[is.na(CleanData$RespCorr),]$ParticipantID`) for which there was an 'NA' value in one of their response columns (we cannot be certain of the source of this 'NA' value so we remove their data entirely to be safe)

B) `r ` participants (IDs = )


```{r 4- Data Exclusion I, warning = FALSE, message = FALSE}

#4A- Excluding any participants for which there are NA values recorded

#i- Look for any 'NA' values in our Response Correctness column
CleanData[is.na(CleanData$RespCorr),]

#ii- Remove participant for whom we have this impossible value
CleanData.RespCorr <- subset(CleanData, ParticipantID != "7gtriiTixvBaQ")

#4B- Excluding any participants with impossible RT values
## Preliminary inspection of data shows trials with negative response time values, which are obviously impossible
RTNegative <- subset(CleanData.RespCorr, RT < 0)

CleanData.RTNegCorr <- subset(CleanData.RespCorr, ParticipantID != "60CBPiTiO1gKw")
CleanData.RTNegCorr <- subset(CleanData.RTNegCorr, ParticipantID != "k3LHwiTiOx7fx")

# Verify that we have removed all negative values RT values from the data frame
RTNegative2 <- subset(CleanData.RTNegCorr, RT < 0)

#2B- Removing Participants with very large single RT values

RTHigh <- subset(CleanData.RespCorr, RT>120000 )

#Relevel this to get rid of factor levels that aren't there any longer
RTHigh$ParticipantID <- factor(RTHigh$ParticipantID)

RTHighs <- as.data.frame(table(RTHigh$ParticipantID))
colnames(RTHighs) <- c("Participant", "Count")

#re-order by count
RTHighs <- RTHighs[order(-RTHighs$Count),]

#Give shorter participantIDs
RTHighs$Participant <- substring(RTHighs$Participant, 1,3)

#Making the Participant Column into an Index
RTHighs2 <- RTHighs[-1]
row.names(RTHighs2) <- RTHighs$Participant

#Transpose for output
RTHighsT <- as.data.frame(t(RTHighs2))

#Get the participantIDs for participants with too-long RT values

participants <- unique(RTHigh$Participant)

#Write a for loop that removes all the lines of the data frame for each of these participants
CleanData.HighRTCorr <- CleanData.RTNegCorr

for (participant in participants) {
  
  CleanData.HighRTCorr <- subset(CleanData.HighRTCorr, ParticipantID != participant)
  
}

CleanData2 <- CleanData.HighRTCorr

# RT Histograms

ggplot(CleanData2, aes(RT)) +
  geom_density() #+
  #xlim(0, 40000)

#Calculating the interquartile range

lowerquart <- quantile(CleanData2$RT)[2]
upperquart <- quantile(CleanData2$RT)[4]

Interquartile <- upperquart - lowerquart

#Calculating thresholds
#Mild thresholds are 1.5* interquartile range
mild.low <- lowerquart - (Interquartile * 1.5)
mild.high <- upperquart + (Interquartile * 1.5)

#Extremes are 3* interquartile range
extreme.low <- lowerquart - (Interquartile * 3)
extreme.high <- upperquart + (Interquartile * 3)


#1- Removing all Outliers ()
CleanData.RTTrim1 <- subset(CleanData2, RT > mild.low & RT < mild.high)

ggplot(CleanData.RTTrim1, aes(RT)) +
  geom_density() +
  ggtitle("Density Plot of RTs- All Outliers Removed")

#2- Replacing all Outliers with the Mean
CleanData.RTTrim2 <- CleanData2

#Compute non-outlier means
NOMean1 <- mean(CleanData.RTTrim1$RT)

CleanData.RTTrim2$RT <- ifelse(CleanData.RTTrim2$RT < mild.low,
                               NOMean1,
                               CleanData.RTTrim2$RT)

CleanData.RTTrim2$RT <- ifelse(CleanData.RTTrim2$RT > mild.high,
                               NOMean1,
                               CleanData.RTTrim2$RT)


ggplot(CleanData.RTTrim2, aes(RT)) +
  geom_density() +
  ggtitle("Density Plot of RTs- All Outliers Replaced with Mean")

#3- Removing only extreme outliers

CleanData.RTTrim3 <- subset(CleanData2, RT > extreme.low & RT < extreme.high)

ggplot(CleanData.RTTrim3, aes(RT)) +
  geom_density() +
  ggtitle("Density Plot of RTs- Extreme Outliers Removed")

#4- Setting outliers to the most extreme of the minimum outlier values

CleanData.RTTrim4 <- CleanData2

CleanData.RTTrim4$RT <- ifelse(CleanData.RTTrim4$RT < mild.low,
                               mild.low,
                               CleanData.RTTrim4$RT)

CleanData.RTTrim4$RT <- ifelse(CleanData.RTTrim4$RT > mild.high,
                               mild.high,
                               CleanData.RTTrim4$RT)

ggplot(CleanData.RTTrim4, aes(RT)) +
  geom_density() +
  ggtitle("Density Plot of RTs- Outliers Trimmed to Mild Outlier Boundary")

#5- Replacing all outliers with the mean on a by-subject basis

participantIDs <- unique(CleanData2$ParticipantID)

participantdata <- list()
CleanData.RTTrim5 <- list()

for (participant in participantIDs) {
  
  participantdata <- subset(CleanData2, ParticipantID == participant)
  
  #Get Non-Outlier Mean
  participantdataNO <- subset(participantdata, RT > mild.low & RT < mild.high)
  NOMean2 <- mean(participantdataNO$RT)
  
  

  participantdata$RT <- ifelse(participantdata$RT < mild.low,
                               NOMean2,
                               participantdata$RT)

  participantdata$RT <- ifelse(participantdata$RT > mild.high,
                                NOMean2,
                               participantdata$RT)
  

  
  CleanData.RTTrim5 <- rbind(CleanData.RTTrim5, participantdata)

}


ggplot(CleanData.RTTrim5, aes(RT)) +
  geom_density() +
  ggtitle("Density Plot of RTs- Outliers Replaced with Mean (By Subject)")

CleanData3 <- CleanData.RTTrim5

```

####Splitting testing trials into new vs. old items (test of generalisation)
```{r Splitting Testing Trials}

#Splitting Testing Trials
participantIDs <- unique(CleanData3$ParticipantID)
participantdata <- list()
participantdata.training <- list()
participantdata.testing <- list()

testingtrials <- list()
trainingtrials <- list()


for (participant in participantIDs) {
  
  participantdata <- subset(CleanData3, ParticipantID == participant)
  participantdata.training <- subset(participantdata, TrialType == "Training")
  participantdata.testing <- subset(participantdata, TrialType == "Testing")
  
  
  TrainingFigures <- unique(participantdata.training$Image)
  
  participantdata.training$Generalisation <- NA
  
  participantdata.testing$Generalisation <- ifelse(
    participantdata.testing$Image %in% TrainingFigures,
    "Old",
    "New")
  
  trainingtrials <- rbind(trainingtrials, participantdata.training)
  testingtrials <- rbind(testingtrials, participantdata.testing)
  
  
}

CleanData4 <- rbind(trainingtrials, testingtrials)


#Factor levels, adding Trial Type 2

CleanData4$TrialType <- factor(CleanData4$TrialType, level = c ("Training", "Testing"))
CleanData4$TrialType2 <- paste(CleanData4$TrialType, CleanData4$Generalisation, sep = "-")
CleanData4$Generalisation <- as.factor(CleanData4$Generalisation)

CleanData4$TrialType2 <- factor(CleanData4$TrialType2, level = c ("Training-NA", "Testing-Old", "Testing-New"),
                                     labels = c("Training", "Testing-Old", "Testing-New"))


# Obtaining the curviness of images from our original script

CleanData4$Image <- sub("Stims/Figures/", "", CleanData4$Image)
CleanData4$Image <- sub(".bmp", "", CleanData4$Image)

CleanData4 <- separate(CleanData4, col=Image, into = c("ImageSeed", "JaggedvsCurved", "Curviness", "Set"), sep = "-")

write.csv(CleanData4, file=("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanDataFinal.csv"))

```

Our experiment is split into Training Trials and Testing Trials, and that is already in the data frame, but there are a few additional differences required.

The first of these is splitting up our testing trials so we can look at Generalisation. Testing trials in this experiment use both the initial set of 16 stimuli per participant and also introduce 8 novel exemplars to test the ability of participants to generalise the rules that they have learned 

The second of these is adding in information about how curvy vs. jagged the various images used are.

Recall that our images were generated along a range of "Curviness" from 0 (Very Jagged) to 30 (Very Curvy) with 10 (somewhat jagged) and 20 (somewhat curvy) also used

We thus used 4 possible pairings of curviness:

0 vs 30
10 vs 20
0 vs 20
10 vs 30

Which means there may be many ways to look at this data.

This is actually already coded in the currently filename structure- so we just need to expand it out into separate columns

#Data Analysis- A First Look
```{r First Look Data Analysis- Replicating Lupyan 2007}

#Name the levels of Condition, rather than having them be numbers
ReplicationData2007 <- subset(CleanData4, Condition == 10|Condition == "3A"|Condition == "3B")

ReplicationData2007$Condition <- factor(ReplicationData2007$Condition,
                            levels= c("3A", "3B", 10),
                            labels = c("Conventional Category","Conventional Category","No Label"))
#There are 2 subconditions here - 3A and 3B - we're going to ignore thedifference for now

Rep2007Agg1 <- aggregate(RespCorr ~ Condition + TrialType + Block , data=ReplicationData2007, mean, na.rm= FALSE)

Rep2007Agg1$Block <- factor(Rep2007Agg1$Block)


```


```{r Reading in the clean data}
#Read in the clean data. This data has had a number of exclusions done on it based on response time and patterns (see the appendices)
CleanData <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanDataFinal.csv")
# Change the order of the Trial Type factor - collapse old and new items
CleanData$TrialType <- factor(CleanData$TrialType, levels = c("Training", "Testing"))
CleanData$TrialType2 <- factor(CleanData$TrialType2, levels = c("Training", "Testing-Old", "Testing-New"))
#Rename our Blocks to see if we can get any models to converge with Blocks
#To do this we need our Testing Blocks to have different names than 1-4, so we go with 10-13 (we can rename these on graphs as we see fit)
CleanData.Testing <- subset(CleanData, TrialType =="Testing")
CleanData.Training <- subset(CleanData, TrialType == "Training")
CleanData.Testing$Block <- mapvalues(CleanData.Testing$Block,
                                     from = c(1,2,3,4),
                                     to = c(10,11,12,13))
CleanData <- rbind(CleanData.Training, CleanData.Testing)
CleanData$BlockF <- factor(CleanData$Block)
CleanData$BlockC <- center_scale(as.numeric(CleanData$Block))
```

# EXPERIMENT 1

```{r Experiment 1 - Lupyan Replication - Data Wrangling}
# Subsetting out only the conditions for the replication
Exp1Data <- subset(CleanData, Condition == 10|Condition == "3A"|Condition == "3B")
# Name the levels of Condition, rather than having them be numbers
# This also collapses subconditions 3A and 3B (justified above)
Exp1Data$Condition2 <- factor(Exp1Data$Condition,
                            levels= c("3A", "3B", 10),
                            labels = c("Conventional Category","Conventional Category","No Label"))
```

## Participants
```{r Experiment 1 - Lupyan Replication - Participants}
count(Exp1Data$Condition) %>%
      data.frame() %>%
        mutate_at("freq", ~ . /240) %>%
          knitr::kable(caption = "Number of Participants per Condition in Experiment 1", ) %>%
              kable_styling(full_width= F)
```

## Subcondition collapse
```{r Experiment 1- Subcondition Collapse}
# Means and SEs of subconditions
Exp1DataSubs <- subset(Exp1Data, Condition2 == "Conventional Category")
Exp1DataSubs$Condition <- factor(Exp1DataSubs$Condition)
Exp1DataSubs %>% 
  summarySE(measurevar = "RespCorr", groupvars = "Condition") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - SubConditions", )
#Sub Condition x Trial Type
Exp1DataSubs %>% 
  summarySE(measurevar = "RespCorr", groupvars = c("Condition", "TrialType")) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - Interaction of SubConditions x Trial Type", )
# MIXED MODEL
afex.Exp1.SC <- mixed(RespCorr ~ Condition * TrialType + (1 |ParticipantID),
                         data=Exp1DataSubs,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
afex.Exp1.SC$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 1 - Subconditions", ) %>%
              kable_styling(full_width= F)
#SUBCONDITION PLOT
Exp1Data.SC.Agg <- summarySE(subset(Exp1Data, Condition2 == "Conventional Category"), measurevar = "RespCorr", groupvars = c("Condition", "TrialType", "BlockF"))
ggplot(data=Exp1Data.SC.Agg, aes(x=BlockF, y=RespCorr, group= Condition)) +
  geom_line(aes(linetype = Condition), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.4,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition") +
  theme_alan() +
  ggtitle("Experiment 1 - Subconditions")

```




## Performance
### Descriptive Statistics
```{r Experiment 1 - Lupyan Replication - Descriptive Statistics, warning = false}
#Means and SEs
Exp1Data.Condition <- 
  summarySE(Exp1Data, measurevar = "RespCorr", groupvars = "Condition2") %>%
    `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci")) 
Exp1Data.TrialType <- 
  summarySE(Exp1Data, measurevar = "RespCorr", groupvars = "TrialType") %>%
    `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci")) 
Exp1Data.Interaction <- 
  summarySE(Exp1Data, measurevar = "RespCorr", groupvars = c("Condition2", "TrialType")) %>%
    unite("Combo", `Condition2`:`TrialType`) %>%
      `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci")) %>%
        mutate(Variable=recode(Variable,
                               `Conventional Category_Training` = "Conventional Category - Training",
                               `Conventional Category_Testing` = "Conventional Category - Testing",
                               `No Label_Training` = "No Label - Training",
                               `No Label_Testing` = "No Label - Training"))
  
  
  
#Bind into a Single DataFram and output as a Kable
Exp1Descriptives <-
  rbind.data.frame(Exp1Data.Condition, Exp1Data.TrialType, Exp1Data.Interaction) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      subset(select = c(Variable, RespCorr, sd)) %>%
        `colnames<-`(c("", "Mean", "sd")) %>%
          knitr::kable(caption = "Experiment 1 - Summary Statistics", ) %>%
            kable_styling(full_width= F) %>%
              pack_rows("Conditions", 1, 2) %>%
                pack_rows("Trial Types", 3, 4) %>%
                  pack_rows("Interactions", 5, 8)
Exp1Descriptives
save_kable(Exp1Descriptives, "Experiment 1- Descriptive Statistics.png")
```

### Mixed Models 
```{r Experiment 1 - Lupyan Replication - Mixed Models, warning = FALSE}
Exp1Data$Block <- as.numeric(Exp1Data$Block)
afex.Exp1 <- mixed(RespCorr ~ Condition2 * TrialType + (1 + Condition2|ParticipantID),
                         data=Exp1Data,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
Exp1Anova <- 
  afex.Exp1$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 1 - Response Data", ) %>%
              kable_styling(full_width= F) 
Exp1Anova
save_kable(Exp1Anova, "Experiment 1- Learning Performance - ANOVA Results.png")
```
#### Mixed Model Post Hoc Comparisons with EM Means
```{r Experiment 1 - Lupyan Replication - EM Means}
#EM MEans
##Blocks vs. Each Other
Exp1.PostHoc <- 
  afex.Exp1 %>% 
  emmeans(~ Condition2 * TrialType)  %>% 
    pairs(adjust = "Tukey") %>% 
      data.frame() %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        knitr::kable(caption = "Experiment 1 - EM Means - Interaction Type", ) %>%
              kable_styling(full_width= F)
Exp1.PostHoc
save_kable(Exp1.PostHoc, "Experiment 1- Learning Performance - Post Hoc Comparisons.png")
```

### Plotted Data

```{r Experiment 1 - Lupyan Replication - Omnibus Plot}
#Aggregate our data for plotting
Exp1Data.Agg <- summarySE(Exp1Data, measurevar = "RespCorr", groupvars = c("Condition2", "TrialType", "BlockF"))
#Plot our data
ggplot(data=Exp1Data.Agg, aes(x=BlockF, y=RespCorr, group= Condition2)) +
  geom_line(aes(linetype = Condition2), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.4,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition") +
  theme_alan()
```


## Response Times

### Descriptive Statistics

```{r Experiment 1 - Resposne Times - Descriptive}
#Means and SEs
Exp1Data.Condition.RT <- 
  summarySE(Exp1Data, measurevar = "RT", groupvars = "Condition2") %>%
    `colnames<-`(c("Variable", "N", "RT", "sd", "se", "ci")) 
Exp1Data.TrialType.RT <- 
  summarySE(Exp1Data, measurevar = "RT", groupvars = "TrialType") %>%
    `colnames<-`(c("Variable", "N", "RT", "sd", "se", "ci")) 
Exp1Data.Interaction.RT <- 
  summarySE(Exp1Data, measurevar = "RT", groupvars = c("Condition2", "TrialType")) %>%
    unite("Combo", `Condition2`:`TrialType`) %>%
      `colnames<-`(c("Variable", "N", "RT", "sd", "se", "ci")) %>%
        mutate(Variable=recode(Variable,
                               `Conventional Category_Training` = "Conventional Category - Training",
                               `Conventional Category_Testing` = "Conventional Category - Testing",
                               `No Label_Training` = "No Label - Training",
                               `No Label_Testing` = "No Label - Training"))
  
  
  
#Bind into a Single DataFrame and output as a Kable
Exp1Descriptives.RT <-
  rbind.data.frame(Exp1Data.Condition.RT, Exp1Data.TrialType.RT, Exp1Data.Interaction.RT) %>%
    mutate_if(is.numeric, round, digits = 2) %>%
      subset(select = c(Variable, RT, sd)) %>%
        `colnames<-`(c("", "Mean", "sd")) %>%
          knitr::kable(caption = "Experiment 1 - Summary Statistics - Response Times", ) %>%
            kable_styling(full_width= F) %>%
              pack_rows("Conditions", 1, 2) %>%
                pack_rows("Trial Types", 3, 4) %>%
                  pack_rows("Interactions", 5, 8)
Exp1Descriptives.RT
save_kable(Exp1Descriptives.RT, "Experiment 1- Descriptive Statistics - RT.png")
```


### Mixed Models
```{r Experiment 1 - Lupyan Replication - Stats - Response Times, warning = FALSE}
afex.Exp1.RT <- mixed(RT ~ Condition2 * TrialType + (1 + Condition2|ParticipantID),
                         data=Exp1Data,
                        control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
Exp1Anova.RT <- 
  afex.Exp1.RT$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 1 - Response Data - RTs", ) %>%
              kable_styling(full_width= F)
Exp1Anova.RT
save_kable(Exp1Anova.RT, "Experiment 1- Learning Performance - ANOVA Results - RTs.png")
```


#### Mixed Model Post Hoc Comparisons with EM Means

```{r RT EMmeans Comparison of Conditions}
#Condition
Exp1.PostHoc.RT <- 
  Exp1Data %>% 
  summarySE(measurevar = "RT", groupvars = "Condition2") %>%
    mutate_if(is.numeric, round, digits = 0) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - Condition - RT", ) 
Exp1.PostHoc.RT
save_kable(Exp1.PostHoc.RT, "Experiment 1- Learning Performance - Post Hoc Comparisons - RTs.png")
```




### Plotted Data

```{r Experiment 1 - Lupyan Replication - Graph 3- Our Data - RTs}
Exp1Data.RT.Agg <- summarySE(Exp1Data, measurevar = "RT", groupvars = c("Condition2", "TrialType", "Block"))
Exp1Data.RT.Agg$Block <- factor(Exp1Data.RT.Agg$Block)
#Plot our data
ggplot(data=Exp1Data.RT.Agg, aes(x=Block, y=RT, group= Condition2)) +
  geom_line(aes(linetype = Condition2), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RT - ci, ymax= RT + ci), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Response Time (ms)") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition") +
  theme_alan() 
```


## Block Effects

### Descriptive Statistics

```{r Experiment 1 - Block Effects - Descriptives}
#Means and SEs
#Condition
Exp1Data.Block.Condition <- 
  subset(Exp1Data, TrialType == "Training")%>% 
    summarySE(measurevar = "RespCorr", groupvars = "Condition2") %>%
      `colnames<-`(c("Variable", "N", "RT", "sd", "se", "ci")) 
#Block
Exp1Data.Block.Block <- 
  subset(Exp1Data, TrialType == "Training")%>% 
    summarySE(measurevar = "RespCorr", groupvars = "Block") %>%
      `colnames<-`(c("Variable", "N", "RT", "sd", "se", "ci")) 
#Interaction
Exp1Data.Block.Interaction <- 
  subset(Exp1Data, TrialType == "Training")%>% 
    summarySE(measurevar = "RespCorr", groupvars = c("Condition2", "Block")) %>%
      subset(select = -Condition2) %>%
      `colnames<-`(c("Variable", "N", "RT", "sd", "se", "ci"))
#Bind into a Single DataFrame, output as a Kable
Exp1Descriptives.Block <- rbind.data.frame(Exp1Data.Block.Condition, Exp1Data.Block.Block, Exp1Data.Block.Interaction) 
Exp1Descriptives.Block$Variable <- c("Conventional Category", "No Label", rep(1:9, 3))
Exp1Descriptives.Block <- Exp1Descriptives.Block %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      subset(select = c(Variable, RT, sd)) %>%
        `colnames<-`(c("", "Mean", "sd")) %>%
          knitr::kable(caption = "Experiment 1 - Summary Statistics - Response Times", ) %>%
            kable_styling(full_width= F) %>%
              pack_rows("Conditions", 1, 2) %>%
                pack_rows("Blocks", 3, 11) %>%
                    pack_rows("Interaction - Conventional Category x Block", 12, 20) %>%
                      pack_rows("Interaction - No Label x Block", 21, 29)
  
Exp1Descriptives.Block
save_kable(Exp1Descriptives.Block, "Experiment 1- Descriptive Statistics - Blocks.png")
```


### Mixed Models

```{r Experiment 1 - Block Effects - Mixed Models, warning = FALSE}
Exp1Data.Training <- subset(Exp1Data, TrialType == "Training")
afex.Exp1.Block <- mixed(RespCorr ~ Condition2 * BlockC + (1+ Condition2|ParticipantID),
                         data=Exp1Data.Training ,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                        method = 'LRT')
Exp1Anova.Block <- 
  afex.Exp1.Block$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 1 - Effect of Block", ) %>%
              kable_styling(full_width= F)
Exp1Anova.Block
save_kable(Exp1Anova.Block, "Experiment 1- Learning Performance - ANOVA Results - Block.png")
```



#### Mixed Model Post Hoc Comparisons with EM Trends

```{r Experiment 1 - Block Effects - EM Trends, warning= FALSE}
Exp1.Trend <- emtrends(afex.Exp1.Block, pairwise ~ Condition2, var = "BlockC")
Exp1.Trend$emtrends %>% 
  data.frame() %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
          `colnames<-`(c("Condition", "Block Trend", "SE", "df", "LCL", "UCL")) %>%
            knitr::kable(caption = "Experiment 1 - Estimated Marginal Trends", ) %>%
              kable_styling(full_width= F)
Exp1.Trend$contrasts %>% 
  data.frame() %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
          mutate_at("p.value", funs(ifelse(.<0.001, "<0.001", .)))%>% 
          `colnames<-`(c("Contrast", "Estimate", "SE", "df", "z ratio", "p")) %>%
            knitr::kable(caption = "Experiment 1 - Comparison of Estimated Marginal Trends", ) %>%
              kable_styling(full_width= F)
```





```{r Experiment 1 - Lupyan Replication - Reading in Gary's Data}
Lupyan2007 <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/RScripts/Lupyan2007Data.csv")
#adding columns we need (filled with NAs) to Gary's data (so the frames can be bound)
Lupyan2007$N <- NA
Lupyan2007$sd <- NA
Lupyan2007$se<- NA
Lupyan2007$ci <- NA
#Adding a "study" column to our data
Exp1Data.Agg2 <- summarySE(Exp1Data, measurevar = "RespCorr", groupvars = c("Condition2", "TrialType", "Block"))
Exp1Data.Agg2$Condition <- Exp1Data.Agg2$Condition2
Exp1Data.Agg2 <- subset(Exp1Data.Agg2, select = -Condition2)
Exp1Data.Agg2$Study <- "Stekic et al (2020)"
#Combining the 2 dataframes into 1
ReplicationAgg2 <- rbind(Exp1Data.Agg2, Lupyan2007)
ReplicationAgg2$Group <- paste(ReplicationAgg2$Study, ReplicationAgg2$Condition)
ReplicationAgg2$Block <- factor(ReplicationAgg2$Block)
```

```{r Experiment 1 - Lupyan Replication - Graph 2 - Comparison - Response Data}
ggplot(data=ReplicationAgg2, aes(x=Block, y=RespCorr, group= Group)) +
  geom_line(aes(linetype = Condition, color = Study), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci, color = Study), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#0066CC", "#CC0033","#33FF00", "#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.40,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  theme_alan()
```













##EXPERIMENT 2

```{r Experiment 2 - Data Wrangling}
# Subsetting out only the conditions for the replication
Exp2Data <- subset(CleanData, Condition == 10|Condition == "3A"|Condition == "3B"|Condition == 1|Condition == 2)
Exp2Data$Condition2 <- factor(Exp2Data$Condition,
                            levels= c(10, 1, 2, "3A", "3B"),
                            labels = c("No Label", "Iconic (Category)", "Counter-Iconic (Category)",
                                       "Conventional (Category)", "Conventional (Category)"))
```

## Participants
```{r Experiment 2 - Participants}
count(Exp2Data$Condition2) %>%
      data.frame() %>%
        mutate_at("freq", ~ . /240) %>%
          knitr::kable(caption = "Number of Participants per Condition in Experiment 2", ) %>%
              kable_styling(full_width= F)
```



## Performance
### Descriptive Statistics
```{r Experiment 2- Descriptive Statistics}
#Means and SEs
#Condition
Exp2Data.Condition <- 
  Exp2Data%>% 
    summarySE(measurevar = "RespCorr", groupvars = "Condition2") %>%
      `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci")) 
#Trial Type
Exp2Data.TrialType <- 
  Exp2Data%>% 
    summarySE(measurevar = "RespCorr", groupvars = "TrialType") %>%
      `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci")) 
#Interaction
Exp2Data.Interaction <- 
  Exp2Data%>% 
    summarySE(measurevar = "RespCorr", groupvars = c("Condition2", "TrialType")) %>%
      subset(select = -Condition2) %>%
      `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci"))
#Bind into a Single DataFrame, output as a Kable
Exp2Descriptives <- rbind.data.frame(Exp2Data.Condition, Exp2Data.TrialType, Exp2Data.Interaction) 
Exp2Descriptives <- 
  Exp2Descriptives %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      subset(select = c(Variable, RespCorr, sd)) %>%
        `colnames<-`(c("", "Mean", "sd")) %>%
          knitr::kable(caption = "Experiment 2 - Summary Statistics", ) %>%
            kable_styling(full_width= F) %>%
              pack_rows("Conditions", 1, 4) %>%
                pack_rows("Trial Types", 5, 6) %>%
                    pack_rows("Interaction - No Label x Trial Type", 7, 8) %>%
                      pack_rows("Interaction - Iconic Category x Trial Type", 9, 10)%>%
                        pack_rows("Interaction - Counter-Iconic Category x Trial Type", 11, 12) %>%
                          pack_rows("Interaction - Conventional Category x Trial Type", 13, 14)
Exp2Descriptives
save_kable(Exp2Descriptives, "Experiment 2- Descriptive Statistics.png")
```

### Mixed Models 
```{r Experiment 2 - Mixed Models, warning = FALSE}
afex.Exp2 <- mixed(RespCorr ~ Condition2 * TrialType + (1 + Condition2|ParticipantID),
                         data=Exp2Data,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
Exp2Anova <- 
  afex.Exp2$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
  
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Part 2", ) %>%
              kable_styling(full_width= F)
Exp2Anova
save_kable(Exp2Anova, "Experiment 2- Learning Performance - ANOVA Results.png")
```
#### Mixed Model Post Hoc Comparisons with EM Means - Condition
```{r Experiment 2 -  EM Means}
##Post-Hoc Effect of Condition
Part2.Condition <- summarySE(data=Exp2Data,
                             measurevar = "RespCorr",
                             groupvars = "Condition2")
Part2.Condition.EM <- emmeans(afex.Exp2, ~Condition2)
##Condition vs. Chance
Part2.Condition.vchance <- test(Part2.Condition.EM, adjust = "none")
##Condition vs. Each Other
Part2.Condition.vPairs <- data.frame(pairs(Part2.Condition.EM, adjust = "none" ))
###NoLabel Baseline
Part2.Condition.vPairs.1 <- 
  rbind(rep(NA,6),Part2.Condition.vPairs[1:3,])
#Iconic Baseline
Part2.Condition.vPairs.2 <- 
  rbind(Part2.Condition.vPairs[1,], rep(NA,6),Part2.Condition.vPairs[4:5,])
#Counter-Iconic Baseline
Part2.Condition.vPairs.3 <- 
  rbind(Part2.Condition.vPairs[2,], Part2.Condition.vPairs[4,], rep(NA,6),Part2.Condition.vPairs[6,])
#Conventional Baseline
Part2.Condition.vPairs.4 <- 
  rbind(Part2.Condition.vPairs[3,],Part2.Condition.vPairs[5,],Part2.Condition.vPairs[6,], rep(NA,6))
###Creating a single dataframe for Blocks
Part2.Condition.Combo <- cbind.data.frame (
  Part2.Condition$Condition, Part2.Condition$RespCorr, Part2.Condition$sd,
  Part2.Condition.vPairs.1$p.value,
  Part2.Condition.vPairs.2$p.value,
  Part2.Condition.vPairs.3$p.value,
  Part2.Condition.vPairs.4$p.value
)
colnames(Part2.Condition.Combo) <- c("Condition", "Mean", "SD", 
                                "No Label",
                                "Iconic",
                                "Counter-Iconic",
                                "Conventional"
                                )
###Knitting Condition Table
Exp2PostHoc.Condition <- 
  Part2.Condition.Combo %>%  
    mutate_if(is.numeric, round, 3) %>%
      mutate_at(.vars = vars("No Label", "Iconic", "Counter-Iconic", "Conventional"),
        funs(ifelse(.<0.001, "<0.001", .))) %>%
          knitr::kable(caption = 'Experiment 2- Post Hoc Comparisons - Condition', "html") %>%
            kable_styling(full_width = F) %>%
              add_header_above(c("", "Descriptive Stats" = 2, 
                "Post-Hoc Comparisons to Other Conditions (p values)" = 4),
                   font_size = 12)
Exp2PostHoc.Condition
save_kable(Exp2PostHoc.Condition, "Experiment 2- Learning Performance - Post-Hoc comparison of Conditions.png")
```

#### Mixed Model Post Hoc Comparisons with EM Means - Interaction
```{r Experiment 2 -  EM Means of Interaction}
#EMMeans of Interaction Terms vs Chance
Part2.Interaction.vChance <- test(emmeans(afex.Exp2, 
                                          ~Condition2 * TrialType,
                                          adjust = "Tukey"))
#EM Means of Interaction Terms vs Each Other
Part2.Interaction.vPairs <- data.frame(pairs(emmeans(afex.Exp2, 
                    ~Condition2 * TrialType,
                    adjust = "Tukey")))
# TRAINING TABLE
#summary Stats
Part2.Condition.Training <- summarySE(data=subset(Exp2Data, TrialType == "Training"),
                             measurevar = "RespCorr",
                             groupvars = "Condition2")
#EM Means comparisons table
Part2.Interaction.vPairs.Training.1 <-   rbind(rep(NA,6),Part2.Interaction.vPairs[1:3,])
Part2.Interaction.vPairs.Training.2 <-   rbind(Part2.Interaction.vPairs[1,], rep(NA, 6),
                                               Part2.Interaction.vPairs[8:9,])
Part2.Interaction.vPairs.Training.3 <-   rbind(Part2.Interaction.vPairs[2,], Part2.Interaction.vPairs[8,],
                                               rep(NA, 6), Part2.Interaction.vPairs[14,])
Part2.Interaction.vPairs.Training.4 <-   rbind(Part2.Interaction.vPairs[3,], Part2.Interaction.vPairs[9,],
                                               Part2.Interaction.vPairs[14,], rep(NA, 6))
Part2.Condition.Combo.Training <- cbind.data.frame (
  Part2.Condition.Training$Condition2, Part2.Condition.Training$RespCorr, Part2.Condition.Training$sd,
  Part2.Interaction.vPairs.Training.1$p.value, Part2.Interaction.vPairs.Training.2$p.value,
  Part2.Interaction.vPairs.Training.3$p.value, Part2.Interaction.vPairs.Training.4$p.value)
colnames(Part2.Condition.Combo.Training) <- c("Condition", "Mean", "SD", 
                                "No Label", "Iconic", "Counter-Iconic", "Conventional"
                                )
# TESTING TABLE
#summary Stats
Part2.Condition.Testing <- summarySE(data=subset(Exp2Data, TrialType == "Testing"),
                             measurevar = "RespCorr",
                             groupvars = "Condition2")
#EM Means comparisons table
Part2.Interaction.vPairs.Testing.1 <-   rbind(rep(NA,6),Part2.Interaction.vPairs[23:25,])
Part2.Interaction.vPairs.Testing.2 <-   rbind(Part2.Interaction.vPairs[23,], rep(NA, 6),
                                               Part2.Interaction.vPairs[26:27,])
Part2.Interaction.vPairs.Testing.3 <-   rbind(Part2.Interaction.vPairs[24,], Part2.Interaction.vPairs[26,],
                                               rep(NA, 6), Part2.Interaction.vPairs[28,])
Part2.Interaction.vPairs.Testing.4 <-   rbind(Part2.Interaction.vPairs[25,], Part2.Interaction.vPairs[27,],
                                               Part2.Interaction.vPairs[28,], rep(NA, 6))
Part2.Condition.Combo.Testing <- cbind.data.frame (
  Part2.Condition.Testing$Condition2, Part2.Condition.Testing$RespCorr, Part2.Condition.Testing$sd,
  Part2.Interaction.vPairs.Testing.1$p.value, Part2.Interaction.vPairs.Testing.2$p.value,
  Part2.Interaction.vPairs.Testing.3$p.value, Part2.Interaction.vPairs.Testing.4$p.value)
colnames(Part2.Condition.Combo.Testing) <- c("Condition", "Mean", "SD", 
                                "No Label",
                                "Iconic",
                                "Counter-Iconic",
                                "Conventional"
                                )
#OUTPUT WHOLE TABLE
OutputTable <- rbind.data.frame(Part2.Condition.Combo.Training, Part2.Condition.Combo.Testing)
Exp2PostHoc.Interaction <- 
  OutputTable %>%
  mutate_if(is.numeric, round, 3) %>%
    mutate_at(.vars = vars("No Label", "Iconic", "Counter-Iconic", "Conventional"),
        funs(ifelse(.<0.001, "<0.001", .))) %>%
          knitr::kable(caption = 'Experiment 2 - Post-Hoc Comparisons - Interaction', "html") %>%
            kable_styling(full_width = F) %>%
              add_header_above(c("", "Descriptive Stats" = 2,  
                                  "Post-Hoc Comparisons between Conditions (p vals)" = 4),
                   font_size = 12) %>%
                pack_rows("Post-Hoc Comparisons of Conditions (Training)", 1, 4) %>%
                  pack_rows("Post-Hoc Comparisons of Conditions (Testing)", 5, 8) 
Exp2PostHoc.Interaction
save_kable(Exp2PostHoc.Interaction, "Experiment 2- Learning Performance - Post-Hoc Exploration of Interactions.png")
```


### Plotted Data

```{r Experiment 2 - Omnibus Plot}
#Aggregate our data for plotting
Exp2Data.Agg <- summarySE(Exp2Data, measurevar = "RespCorr", groupvars = c("Condition2", "TrialType", "BlockF"))
#Plot our data
ggplot(data=Exp2Data.Agg, aes(x=BlockF, y=RespCorr, group= Condition2)) +
  geom_line(aes(linetype = Condition2, color= Condition2), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci, color = Condition2), width= 0.2, size = 1, position=pd) +
  scale_color_manual(values= c("#000000", "#007e70","#00b19d", "#00e4ca")) +
  scale_linetype_manual(values = c("dashed", rep("solid",3))) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.4,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition", color = "Condition") +
  theme_alan()
```


## Response Times

### Descriptive Statistics

```{r Experiment 2 - Resposne Times - Descriptive}
#Condition
Exp2Data %>% 
  summarySE(measurevar = "RT", groupvars = "Condition2") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - Condition", )
#Trial Type
Exp2Data %>% 
  summarySE(measurevar = "RT", groupvars = "TrialType") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - Trial Type", )
#Condition x Trial Type
Exp2Data %>% 
  summarySE(measurevar = "RT", groupvars = c("Condition2", "TrialType")) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - Interaction of Condition x Trial Type", )
```


### Mixed Models
```{r Experiment 2 - Stats - Response Times, warning = FALSE}
afex.Exp2.RT <- mixed(RT ~ Condition2 * TrialType + (1 + Condition2|ParticipantID),
                         data=Exp2Data,
                      control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
afex.Exp2.RT$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 1 - Response Data - RTs", ) %>%
              kable_styling(full_width= F)
```


#### Mixed Model Post Hoc Comparisons with EM Means

```{r EXP2 - RT EMmeans Comparison of Conditions}
#Condition
Exp2Data %>% 
  summarySE(measurevar = "RT", groupvars = "Condition2") %>%
    mutate_if(is.numeric, round, digits = 0) %>%
      knitr::kable(caption = "Experiment 2 - Summary Statistics - Condition - RT", )
```



### Plotted Data

```{r Experiment 2 - Graph 3- Our Data - RTs}
Exp2Data.RT.Agg <- summarySE(Exp2Data, measurevar = "RT", groupvars = c("Condition2", "TrialType", "Block"))
Exp2Data.RT.Agg$Block <- factor(Exp1Data.RT.Agg$Block)
#Plot our data
ggplot(data=Exp2Data.RT.Agg, aes(x=Block, y=RT, group= Condition2)) +
  geom_line(aes(linetype = Condition2), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RT - ci, ymax= RT + ci), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Response Time (ms)") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition") +
  theme_alan() +
  ggtitle("Experiment 2 - Response Times")
```


## Block Effects

### Descriptive Statistics

```{r Experiment 2 - Block Effects - Descriptives}
#Condition
subset(Exp2Data, TrialType == "Training") %>% 
  summarySE(measurevar = "RespCorr", groupvars = "Condition2") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - Training - Condition -", )
#Interaction
subset(Exp2Data, TrialType == "Training") %>% 
  summarySE(measurevar = "RespCorr", groupvars = c("Block", "Condition2")) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 1 - Summary Statistics - Training -  Interaction -", )
```


### Mixed Models

```{r Experiment 2 - Block Effects - Mixed Models, warning = FALSE}
Exp2Data.Training <- subset(Exp2Data, TrialType == "Training")
afex.Exp2.Block <- mixed(RespCorr ~ Condition2  * BlockC + (1|ParticipantID),
                         data=Exp2Data.Training ,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                        method = 'LRT')
afex.Exp2.Block$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 2 - Effect of Block", ) %>%
              kable_styling(full_width= F)
```



#### Mixed Model Post Hoc Comparisons with EM Trends

```{r Experiment 2 - Block Effects - EM Trends, warning= FALSE}
Exp2.Trend <- emtrends(afex.Exp2.Block, pairwise ~ Condition2, var = "BlockC", adjust = "Tukey")
Exp2.Trend$emtrends %>% 
  data.frame() %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
          `colnames<-`(c("Condition", "Block Trend", "SE", "df", "LCL", "UCL")) %>%
            knitr::kable(caption = "Experiment 1 - Estimated Marginal Trends", ) %>%
              kable_styling(full_width= F)
Exp2.Trend$contrasts %>% 
  data.frame() %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
          mutate_at("p.value", funs(ifelse(.<0.001, "<0.001", .)))%>% 
          `colnames<-`(c("Contrast", "Estimate", "SE", "df", "z ratio", "p")) %>%
            knitr::kable(caption = "Experiment 1 - Comparison of Estimated Marginal Trends", ) %>%
              kable_styling(full_width= F)
emmip(afex.Exp2.Block, Condition2 ~ BlockC, cov.reduce = range)
```


















##EXPERIMENT 3

```{r Experiment 3 - Data Wrangling}
Exp3Data <- subset(CleanData, Condition == 10|Condition == 4|Condition == 5|Condition == "6A"|Condition == "6B"
                    |Condition == 7|Condition == 8|Condition == 9)
Exp3Data$Condition2 <- factor(Exp3Data$Condition,
                            levels= c(10, 4, 5, "6A", "6B", 7, 8, 9),
                            labels = c("No Label", "Iconic Item", "Counter-Iconic Item", "Conventional Item", "Conventional Item",
                                       rep("Arbitrary",3)))
```

## Participants
```{r Experiment 3 - Participants}
count(Exp3Data$Condition2) %>%
      data.frame() %>%
        mutate_at("freq", ~ . /240) %>%
          knitr::kable(caption = "Number of Participants per Condition in Experiment 3", ) %>%
              kable_styling(full_width= F)
```

## Subcondition collapse - Conventional Item Labels (6A and B8)
```{r Experiment 3- Subcondition Collapse - Conventional Items}
# Means and SEs of subconditions
Exp3DataSubs.Conventional <- subset(Exp3Data, Condition2 == "Conventional Item")
Exp3DataSubs.Conventional$Condition <- factor(Exp3DataSubs.Conventional$Condition)
Exp3DataSubs.Conventional %>% 
  summarySE(measurevar = "RespCorr", groupvars = "Condition") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - SubConditions of Conventional Items", )
#Sub Condition x Trial Type
Exp3DataSubs.Conventional %>% 
  summarySE(measurevar = "RespCorr", groupvars = c("Condition", "TrialType")) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics (Conventional Items) - Interaction of SubConditions x Trial Type", )
# MIXED MODEL
afex.Exp3.SC1 <- mixed(RespCorr ~ Condition * TrialType + (1 |ParticipantID),
                         data=Exp3DataSubs.Conventional,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
afex.Exp3.SC1$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 3 - Subconditions of Conventional Items", ) %>%
              kable_styling(full_width= F)
#SUBCONDITION PLOT
Exp3Data.SC1.Agg <- summarySE(Exp3DataSubs.Conventional, measurevar = "RespCorr", groupvars = c("Condition", "TrialType", "BlockF"))
ggplot(data=Exp3Data.SC1.Agg, aes(x=BlockF, y=RespCorr, group= Condition)) +
  geom_line(aes(linetype = Condition), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.4,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition") +
  theme_alan()
```


## Subcondition collapse - Arbitrary Item Labels (Conditions 7,8,9)
```{r Experiment 3- Subcondition Collapse}
# Means and SEs of subconditions
Exp3DataSubs.Arbitrary <- subset(Exp3Data, Condition2 == "Arbitrary")
Exp3DataSubs.Arbitrary$Condition <- factor(Exp3DataSubs.Arbitrary$Condition)
Exp3DataSubs.Arbitrary %>% 
  summarySE(measurevar = "RespCorr", groupvars = "Condition") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - SubConditions of Arbitrary Items", )
#Sub Condition x Trial Type
Exp3DataSubs.Arbitrary %>% 
  summarySE(measurevar = "RespCorr", groupvars = c("Condition", "TrialType")) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics (Arbitrary Items) - Interaction of SubConditions x Trial Type", )
# MIXED MODEL
afex.Exp3.SC2 <- mixed(RespCorr ~ Condition * TrialType + (1 |ParticipantID),
                         data=Exp3DataSubs.Arbitrary,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
afex.Exp3.SC2$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 3 - Subconditions of Arbitrary Items", ) %>%
              kable_styling(full_width= F)
#SUBCONDITION PLOT
Exp3Data.SC2.Agg <- summarySE(Exp3DataSubs.Arbitrary, measurevar = "RespCorr", groupvars = c("Condition", "TrialType", "BlockF"))
ggplot(data=Exp3Data.SC2.Agg, aes(x=BlockF, y=RespCorr, group= Condition)) +
  geom_line(aes(linetype = Condition), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.4,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition") +
  theme_alan()
```





## Performance
### Descriptive Statistics
```{r Experiment 3- Descriptive Statistics}
#Means and SEs
#Condition
Exp3Data.Condition <- 
  Exp3Data%>% 
    summarySE(measurevar = "RespCorr", groupvars = "Condition2") %>%
      `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci")) 
#Trial Type
Exp3Data.TrialType <- 
  Exp3Data%>% 
    summarySE(measurevar = "RespCorr", groupvars = "TrialType") %>%
      `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci")) 
#Interaction
Exp3Data.Interaction <- 
  Exp3Data%>% 
    summarySE(measurevar = "RespCorr", groupvars = c("Condition2", "TrialType")) %>%
      subset(select = -Condition2) %>%
      `colnames<-`(c("Variable", "N", "RespCorr", "sd", "se", "ci"))
Exp3Descriptives <- rbind.data.frame(Exp3Data.Condition, Exp3Data.TrialType, Exp3Data.Interaction) 
Exp3Descriptives <- 
  Exp3Descriptives %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      subset(select = c(Variable, RespCorr, sd)) %>%
        `colnames<-`(c("", "Mean", "sd")) %>%
          knitr::kable(caption = "Experiment 3 - Summary Statistics", ) %>%
            kable_styling(full_width= F) %>%
              pack_rows("Conditions", 1, 5) %>%
                pack_rows("Trial Types", 6, 7) %>%
                    pack_rows("Interaction - No Label x Trial Type", 8, 9) %>%
                      pack_rows("Interaction - Iconic Item x Trial Type", 10, 11)%>%
                        pack_rows("Interaction - Counter-Iconic Item x Trial Type", 12, 13) %>%
                          pack_rows("Interaction - Conventional Item x Trial Type", 14, 15)%>%
                            pack_rows("Interaction - Arbitrary x Trial Type", 16, 17)
Exp3Descriptives
save_kable(Exp3Descriptives, "Experiment 3- Descriptive Statistics.png")
```

### Mixed Models 
```{r Experiment 3 - Mixed Models, warning = FALSE}
afex.Exp3 <- mixed(RespCorr ~ Condition2 * TrialType + (1 + Condition2|ParticipantID),
                         data=Exp3Data,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
Exp3Anova <- 
  afex.Exp3$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 3", ) %>%
              kable_styling(full_width= F)
Exp3Anova
save_kable(Exp3Anova, "Experiment 3- Learning Performance - ANOVA Results.png")
```
#### Mixed Model Post Hoc Comparisons with EM Means - Condition
```{r Experiment 3 -  EM Means}
##Post-Hoc Effect of Condition
Exp3.Condition <- summarySE(data=Exp3Data,
                             measurevar = "RespCorr",
                             groupvars = "Condition2")
Exp3.Condition.EM <- emmeans(afex.Exp3, ~Condition2)
##Condition vs. Chance
Exp3.Condition.vchance <- test(Exp3.Condition.EM, adjust = "none")
##Condition vs. Each Other
Exp3.Condition.vPairs <- data.frame(pairs(Exp3.Condition.EM, adjust = "none" ))
###NoLabel Baseline
Exp3.Condition.vPairs.1 <- 
  rbind(rep(NA,6),Exp3.Condition.vPairs[1:4,])
#Iconic Baseline
Exp3.Condition.vPairs.2 <- 
  rbind(Exp3.Condition.vPairs[1,], rep(NA,6),Exp3.Condition.vPairs[5:7,])
#Counter-Iconic Baseline
Exp3.Condition.vPairs.3 <- 
  rbind(Exp3.Condition.vPairs[2,], Exp3.Condition.vPairs[5,], rep(NA,6),Exp3.Condition.vPairs[8:9,])
#Conventional Baseline
Exp3.Condition.vPairs.4 <- 
  rbind(Exp3.Condition.vPairs[3,],Exp3.Condition.vPairs[6,],Exp3.Condition.vPairs[8,], rep(NA,6), Exp3.Condition.vPairs[10,])
#Arbitrary Baseline
Exp3.Condition.vPairs.5 <- 
  rbind(Exp3.Condition.vPairs[4,],Exp3.Condition.vPairs[7,],Exp3.Condition.vPairs[9:10,], rep(NA,6))
###Creating a single dataframe for Blocks
Exp3.Condition.Combo <- cbind.data.frame (
  Exp3.Condition$Condition, Exp3.Condition$RespCorr, Exp3.Condition$sd,
  Exp3.Condition.vPairs.1$p.value,
  Exp3.Condition.vPairs.2$p.value,
  Exp3.Condition.vPairs.3$p.value,
  Exp3.Condition.vPairs.4$p.value,
  Exp3.Condition.vPairs.5$p.value
)
colnames(Exp3.Condition.Combo) <- c("Condition", "Mean", "SD", 
                                "No Label",
                                "Iconic",
                                "Counter-Iconic",
                                "Conventional",
                                "Arbitrary"
                                )
###Knitting Condition Table
Exp3PostHoc.Condition <- 
  Exp3.Condition.Combo %>%  
    mutate_if(is.numeric, round, 3) %>%
      mutate_at(.vars = vars("No Label", "Iconic", "Counter-Iconic", "Conventional", "Arbitrary"),
        funs(ifelse(.<0.001, "<0.001", .))) %>%
          knitr::kable(caption = 'Experiment 3- Post Hoc Comparisons - Condition', "html") %>%
            kable_styling(full_width = F) %>%
              add_header_above(c("", "Descriptive Stats" = 2, 
                "Post-Hoc Comparisons to Other Conditions (p values)" = 5),
                   font_size = 12)
Exp3PostHoc.Condition
save_kable(Exp3PostHoc.Condition, "Experiment 3- Learning Performance - Post-Hoc comparison of Conditions.png")
```

#### Mixed Model Post Hoc Comparisons with EM Means - Interaction
```{r Experiment 3 -  EM Means of Interaction}
#EMMeans of Interaction Terms vs Chance
Exp3.Interaction.vChance <- test(emmeans(afex.Exp3, 
                                          ~Condition2 * TrialType,
                                          adjust = "Tukey"))
#EM Means of Interaction Terms vs Each Other
Exp3.Interaction.vPairs <- data.frame(pairs(emmeans(afex.Exp3, 
                    ~Condition2 * TrialType,
                    adjust = "Tukey")))
# TRAINING TABLE
#summary Stats
Exp3.Condition.Training <- summarySE(data=subset(Exp3Data, TrialType == "Training"),
                             measurevar = "RespCorr",
                             groupvars = "Condition2")
#EM Means comparisons table
#No Label baseline
Exp3.Interaction.vPairs.Training.1 <-   rbind(rep(NA,6),Exp3.Interaction.vPairs[1:4,])
#Iconic Baseline
Exp3.Interaction.vPairs.Training.2 <- 
  rbind(Exp3.Interaction.vPairs[1,], rep(NA,6),Exp3.Interaction.vPairs[10:12,])
#Counter-Iconic Baseline
Exp3.Interaction.vPairs.Training.3 <- 
  rbind(Exp3.Interaction.vPairs[2,], Exp3.Interaction.vPairs[10,], rep(NA,6),Exp3.Interaction.vPairs[18:19,])
#Conventional Baseline
Exp3.Interaction.vPairs.Training.4 <- 
  rbind(Exp3.Interaction.vPairs[3,],Exp3.Interaction.vPairs[11,],Exp3.Interaction.vPairs[18,], rep(NA,6), Exp3.Interaction.vPairs[25,])
#Arbitrary Baseline
Exp3.Interaction.vPairs.Training.5 <- 
  rbind(Exp3.Interaction.vPairs[4,],Exp3.Interaction.vPairs[12,],Exp3.Interaction.vPairs[19,], Exp3.Interaction.vPairs[25,], rep(NA,6))
###Creating a single dataframe for Blocks
Exp3.Condition.Combo.Training <- cbind.data.frame (
  Exp3.Condition.Training$Condition, Exp3.Condition.Training$RespCorr, Exp3.Condition.Training$sd,
  Exp3.Interaction.vPairs.Training.1$p.value,
  Exp3.Interaction.vPairs.Training.2$p.value,
  Exp3.Interaction.vPairs.Training.3$p.value,
  Exp3.Interaction.vPairs.Training.4$p.value,
  Exp3.Interaction.vPairs.Training.5$p.value
)
colnames(Exp3.Condition.Combo.Training) <- c("Condition", "Mean", "SD", 
                                "No Label", "Iconic", "Counter-Iconic", "Conventional", "Arbitrary"
                                )
# TESTING TABLE
#summary Stats
Exp3.Condition.Testing <- summarySE(data=subset(Exp3Data, TrialType == "Testing"),
                             measurevar = "RespCorr",
                             groupvars = "Condition2")
#EM Means comparisons table
#NoLabel Baseline
Exp3.Interaction.vPairs.Testing.1 <-   rbind(rep(NA,6),Exp3.Interaction.vPairs[36:39,])
#Iconic Baseline
Exp3.Interaction.vPairs.Testing.2 <- 
  rbind(Exp3.Interaction.vPairs[36,], rep(NA,6),Exp3.Interaction.vPairs[40:42,])
#Counter-Iconic Baseline
Exp3.Interaction.vPairs.Testing.3 <- 
  rbind(Exp3.Interaction.vPairs[37,], Exp3.Interaction.vPairs[40,], rep(NA,6),Exp3.Interaction.vPairs[43:44,])
#Conventional Baseline
Exp3.Interaction.vPairs.Testing.4 <- 
  rbind(Exp3.Interaction.vPairs[38,],Exp3.Interaction.vPairs[41,],Exp3.Interaction.vPairs[43,], rep(NA,6), Exp3.Interaction.vPairs[45,])
#Arbitrary Baseline
Exp3.Interaction.vPairs.Testing.5 <- 
  rbind(Exp3.Interaction.vPairs[39,],Exp3.Interaction.vPairs[42,],Exp3.Interaction.vPairs[44,], Exp3.Interaction.vPairs[45,], rep(NA,6))
###Creating a single dataframe for Blocks
Exp3.Condition.Combo.Testing <- cbind.data.frame (
  Exp3.Condition.Testing$Condition, Exp3.Condition.Testing$RespCorr, Exp3.Condition.Testing$sd,
  Exp3.Interaction.vPairs.Testing.1$p.value,
  Exp3.Interaction.vPairs.Testing.2$p.value,
  Exp3.Interaction.vPairs.Testing.3$p.value,
  Exp3.Interaction.vPairs.Testing.4$p.value,
  Exp3.Interaction.vPairs.Testing.5$p.value
)
colnames(Exp3.Condition.Combo.Testing) <- c("Condition", "Mean", "SD", 
                                "No Label", "Iconic", "Counter-Iconic", "Conventional", "Arbitrary"
                                )
#OUTPUT WHOLE TABLE
OutputTable <- rbind.data.frame(Exp3.Condition.Combo.Training, Exp3.Condition.Combo.Testing)
Exp3PostHoc.Interaction <- 
  OutputTable %>%
  mutate_if(is.numeric, round, 3) %>%
    mutate_at(.vars = vars("No Label", "Iconic", "Counter-Iconic", "Conventional", "Arbitrary"),
        funs(ifelse(.<0.001, "<0.001", .))) %>%
          knitr::kable(caption = 'Experiment 3 - Post-Hoc Comparisons - Interaction', "html") %>%
            kable_styling(full_width = F) %>%
              add_header_above(c("", "Descriptive Stats" = 2,  
                                  "Post-Hoc Comparisons between Conditions (p vals)" = 5),
                   font_size = 12) %>%
                pack_rows("Post-Hoc Comparisons of Conditions (Training)", 1, 5) %>%
                  pack_rows("Post-Hoc Comparisons of Conditions (Testing)", 6, 10) 
Exp3PostHoc.Interaction
save_kable(Exp3PostHoc.Interaction, "Experiment 3- Learning Performance - Post-Hoc Exploration of Interactions.png")
```


### Plotted Data

```{r Experiment 3 - Omnibus Plot}
#Aggregate our data for plotting
Exp3Data.Agg <- summarySE(Exp3Data, measurevar = "RespCorr", groupvars = c("Condition2", "TrialType", "BlockF"))
#Plot our data
ggplot(data=Exp3Data.Agg, aes(x=BlockF, y=RespCorr, group= Condition2)) +
  geom_line(aes(linetype = Condition2, color= Condition2), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci, color = Condition2), width= 0.2, size = 1, position=pd) +
  scale_color_manual(values= c("#000000", "#c144c1","#8b2e8b", "#652165", "gray")) +
  scale_linetype_manual(values = c(rep("dashed",5))) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.4,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition", color = "Condition") +
  theme_alan()
```


## Response Times

### Descriptive Statistics

```{r Experiment 3 - Resposne Times - Descriptive}
#Condition
Exp3Data %>% 
  summarySE(measurevar = "RT", groupvars = "Condition2") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - Condition - RT", )
#Trial Type
Exp3Data %>% 
  summarySE(measurevar = "RT", groupvars = "TrialType") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - Trial Type - RT", )
#Condition x Trial Type
Exp3Data %>% 
  summarySE(measurevar = "RT", groupvars = c("Condition2", "TrialType")) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - Interaction of Condition x Trial Type - RT", )
```


### Mixed Models
```{r Experiment 3 - Stats - Response Times, warning = FALSE}
afex.Exp3.RT <- mixed(RT ~ Condition2 * TrialType + (1 + Condition2|ParticipantID),
                         data=Exp3Data,
                      control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                         method = 'LRT')
#Pretty up results and kick out as kable
afex.Exp3.RT$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 3 - Response Data - RTs", ) %>%
              kable_styling(full_width= F)
```


#### Mixed Model Post Hoc Comparisons with EM Means

```{r EXP3 - RT EMmeans Comparison of Conditions}
#Condition
Exp3Data %>% 
  summarySE(measurevar = "RT", groupvars = "Condition2") %>%
    mutate_if(is.numeric, round, digits = 0) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - Condition - RT", )
```



### Plotted Data

```{r Experiment 3 - Graph 3- Our Data - RTs}
Exp3Data.RT.Agg <- summarySE(Exp3Data, measurevar = "RT", groupvars = c("Condition2", "TrialType", "Block"))
Exp3Data.RT.Agg$Block <- factor(Exp3Data.RT.Agg$Block)
#Plot our data
ggplot(data=Exp3Data.RT.Agg, aes(x=Block, y=RT, group= Condition2)) +
  geom_line(aes(linetype = Condition2), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RT - ci, ymax= RT + ci), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Response Time (ms)") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  labs(linetype = "Condition") +
  theme_alan()
```


## Block Effects

### Descriptive Statistics

```{r Experiment 3 - Block Effects - Descriptives}
#Condition
subset(Exp3Data, TrialType == "Training") %>% 
  summarySE(measurevar = "RespCorr", groupvars = "Condition2") %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - Training - Condition -", )
#Interaction
subset(Exp3Data, TrialType == "Training") %>% 
  summarySE(measurevar = "RespCorr", groupvars = c("Block", "Condition2")) %>%
    mutate_if(is.numeric, round, digits = 3) %>%
      knitr::kable(caption = "Experiment 3 - Summary Statistics - Training -  Interaction -", )
```


### Mixed Models

```{r Experiment 3 - Block Effects - Mixed Models, warning = FALSE}
Exp3Data.Training <- subset(Exp3Data, TrialType == "Training")
afex.Exp3.Block <- mixed(RespCorr ~ Condition2  * BlockC + (1|ParticipantID),
                         data=Exp3Data.Training ,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)),
                        method = 'LRT')
afex.Exp3.Block$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Mixed Model Results - Experiment 3 - Effect of Block", ) %>%
              kable_styling(full_width= F)
```



#### Mixed Model Post Hoc Comparisons with EM Trends

```{r Experiment 3 - Block Effects - EM Trends, warning= FALSE}
Exp3.Trend <- emtrends(afex.Exp3.Block, pairwise ~ Condition2, var = "BlockC", adjust = "Tukey")
Exp3.Trend$emtrends %>% 
  data.frame() %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
          `colnames<-`(c("Condition", "Block Trend", "SE", "df", "LCL", "UCL")) %>%
            knitr::kable(caption = "Experiment 3 - Estimated Marginal Trends", ) %>%
              kable_styling(full_width= F)
Exp3.Trend$contrasts %>% 
  data.frame() %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
          mutate_at("p.value", funs(ifelse(.<0.001, "<0.001", .)))%>% 
          `colnames<-`(c("Contrast", "Estimate", "SE", "df", "z ratio", "p")) %>%
            knitr::kable(caption = "Experiment 3 - Comparison of Estimated Marginal Trends", ) %>%
              kable_styling(full_width= F)
##Output as a nice table
Exp3EMTrends <- data.frame(Exp3.Trend$emtrend)
Exp3EMContrasts <- data.frame(Exp3.Trend$contrasts)
###NoLabel Baseline
Exp3EMContrasts.1 <- 
  rbind(rep(NA,6),Exp3EMContrasts[1:4,])
#Iconic Baseline
Exp3EMContrasts.2 <- 
  rbind(Exp3EMContrasts[1,], rep(NA,6),Exp3EMContrasts[5:7,])
#Counter-Iconic Baseline
Exp3EMContrasts.3 <- 
  rbind(Exp3EMContrasts[2,], Exp3EMContrasts[5,], rep(NA,6),Exp3EMContrasts[8:9,])
#Conventional Baseline
Exp3EMContrasts.4 <- 
  rbind(Exp3EMContrasts[3,],Exp3EMContrasts[6,],Exp3EMContrasts[8,], rep(NA,6), Exp3EMContrasts[10,])
#Arbitrary Baseline
Exp3EMContrasts.5 <- 
  rbind(Exp3EMContrasts[4,],Exp3EMContrasts[7,],Exp3EMContrasts[9:10,], rep(NA,6))
###Creating a single dataframe for Blocks
Exp3.EMContrasts.Combo <- 
  cbind.data.frame (
  Exp3EMTrends$Condition2, Exp3EMTrends$BlockC.trend, Exp3EMTrends$SE,
  Exp3EMContrasts.1$p.value,
  Exp3EMContrasts.2$p.value,
  Exp3EMContrasts.3$p.value,
  Exp3EMContrasts.4$p.value,
  Exp3EMContrasts.4$p.value
)
colnames(Exp3.EMContrasts.Combo) <- c("Condition", "Slope", "SE", 
                                "No Label",
                                "Iconic",
                                "Counter-Iconic",
                                "Conventional",
                                "Arbitrary"
                                )
###Knitting Condition Table
Exp3.EMContrasts.Combo <- 
  Exp3.EMContrasts.Combo %>%  
    mutate_if(is.numeric, round, 3) %>%
      mutate_at(.vars = vars("No Label", "Iconic", "Counter-Iconic", "Conventional", "Arbitrary"),
        funs(ifelse(.<0.001, "<0.001", .))) %>%
          knitr::kable(caption = 'Experiment 3- Post Hoc Comparisons of Estimated Marginal Trends', "html") %>%
            kable_styling(full_width = F) %>%
              add_header_above(c("", "Descriptive Stats" = 2, 
                "Post-Hoc Comparisons to Other Conditions (p values)" = 5),
                   font_size = 12)
Exp3.EMContrasts.Combo
save_kable(Exp3.EMContrasts.Combo, "Experiment 3- Learning Performance - Post-Hoc comparison of Estimated Marginal Trends.png")
emmip(afex.Exp3.Block, Condition2 ~ BlockC, cov.reduce = range)
```









##OMNIBUS ANALYSIS

For the final part of the study, we bring everything from the above together, making use of a factorial approach to look for effects of iconicity, systematicity, and label type

In this, we're going to look only at Training trials (because testing trials haven't told us anything interesting so far).




```{r Omnibus - Data Wrangling}
Exp4Data <- CleanData.Training
Exp4Data$Condition <- as.factor(Exp4Data$Condition)
conditions <- levels(Exp4Data$Condition)
#Label Type Column
Exp4Data$LabelType <- mapvalues(Exp4Data$Condition,
                                 from = conditions,
                                 to = c("Category", "No Label", rep("Category", 3), rep("Item", 7)))
Exp4Data$LabelType <- factor(Exp4Data$LabelType, levels = c("No Label", "Category", "Item"))
#Systematicity Column
Exp4Data$Systematicity <- mapvalues(Exp4Data$Condition,
                                 from = conditions,
                                 to = c("Non-Systematic", "No Label", rep("Non-Systematic", 3), rep("Systematic", 4), rep("Non-Systematic",3)))
Exp4Data$Systematicity <- factor(Exp4Data$Systematicity, levels = c("No Label", "Systematic", "Non-Systematic"))
#Iconicity Column
Exp4Data$Iconicity <- mapvalues(Exp4Data$Condition,
                                 from = conditions,
                                 to = c("Iconic", "No Label", "Counter-Iconic", "Conventional", "Conventional", "Iconic", "Counter-Iconic",
                                        rep("Conventional", 5)))
Exp4Data$Iconicity <- factor(Exp4Data$Iconicity, levels = c("No Label", "Iconic", "Counter-Iconic", "Conventional"))
```

### Plotted Data

```{r Experiment 4 - Omnibus Plot}
#Aggregate our data for plotting
Exp4Data$Collapse <- paste(Exp4Data$LabelType, Exp4Data$Systematicity, Exp4Data$Iconicity, sep = ":")
Exp4Data$Collapse <- factor(Exp4Data$Collapse, 
                             levels = c(
                               "No Label:No Label:No Label",
                                "Category:Non-Systematic:Iconic", 
                                "Category:Non-Systematic:Counter-Iconic",
                                "Category:Non-Systematic:Conventional",
                                "Item:Systematic:Iconic",
                                "Item:Systematic:Counter-Iconic",
                                "Item:Systematic:Conventional",
                                "Item:Non-Systematic:Conventional"
                               ),
                             labels = c(
                                "No Labels",
                                "Iconic Category Labels", 
                                "Counter-Iconic Category Labels",
                                "Conventional Category Labels",
                                "Iconic Item Labels",
                                "Counter-Iconic Item Labels",
                                "Conventional Item Labels",
                                "Arbitrary Labels"
                               )
                            )
Exp4Agg <- summarySE(Exp4Data, measurevar = "RespCorr", groupvars = c("Block", "Collapse"))
Exp4Agg$Block <- factor(Exp4Agg$Block)
#Plot our data
ggplot(data=Exp4Agg, aes(x=Block, y=RespCorr, group= Collapse)) +
  geom_line(aes(linetype = Collapse, color = Collapse), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci, color= Collapse), width= 0.2, size = 1, position=pd)+
  scale_color_manual(name = "Condition", 
                     values= c("black", 
                               "#007e70", "#00b19d", "#00e4ca", 
                               "#c144c1", "#8b2e8b", "#652165", 
                               "gray")) +
  scale_linetype_manual(name = "Condition",
                        values = c("dashed", rep("solid",3), rep("dashed",4))) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.40,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  #facet_grid(~LabelType) +
  theme_alan() 
```

So maybe that doesn't show us anything super exciting - or rather its hard to read. Because we don't actually plot Label Type Here.

But we know from our omnibus analysis that level of Iconicity makes no difference (and of course we saw that in all other analyses), so lets get rid of iconicity and instead plot Label Type vs Systematicity


```{r Experiment 4 - Label Type x Systematicity Plot}
Exp4Data$Collapse2 <- paste(Exp4Data$LabelType, Exp4Data$Systematicity, sep = ":")
Exp4Data$Collapse2 <- factor(Exp4Data$Collapse2, 
                             levels = 
                               c("Category:Non-Systematic",
                                 "Item:Systematic",
                                "Item:Non-Systematic",
                                 "No Label:No Label"),
                             labels = 
                               c("Category Labels",
                                 "Item Labels (Systematic)",
                                 "Arbitrary Labels",
                                 "No Labels"))
Exp4Agg2 <- summarySE(Exp4Data, measurevar = "RespCorr", groupvars = c("Block", "Collapse2", "Systematicity", "LabelType"))
Exp4Agg2$Block <- factor(Exp4Agg2$Block)
#Plot our data
ggplot(data=Exp4Agg2, aes(x=Block, y=RespCorr, group= Collapse2)) +
  geom_line(aes(linetype = Collapse2, color = Collapse2), size = 1.2, position=pd) +
  geom_errorbar(aes(ymin= RespCorr - ci, ymax= RespCorr + ci, color= Collapse2), width= 0.2, size = 1, position=pd)+
  scale_color_manual(values= c("#00b19d", "#8b2e8b","gray", "black")) +
  scale_linetype_manual(values = c(rep("solid", 2), "dashed", "dashed")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.40,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  theme_alan() +
  labs(color = "Label Type", linetype = "Label Type")
```


In order to get some sensible EMmeans comparisons out, we're now going to re-write our ANOVA to use the Collapsed conditions shown in the figure above


```{r Experiment 4 - Mixed Models II, warning = FALSE}
afex.Exp4.2 <- mixed(RespCorr ~ Collapse2 + (1|ParticipantID),
                         data=Exp4Data,
                         method = 'LRT')
#Pretty up results and kick out as kable
Exp4Anova2 <-
  afex.Exp4.2$anova_table %>% 
  data.frame() %>% 
    tibble::rownames_to_column(var= "Variable") %>% 
      mutate_if(is.numeric, round, digits = 3) %>% 
        mutate_all(funs(ifelse(.<0.001, "<0.001", .))) %>%
          `colnames<-`(c("Variable", "df", "Chi Sq", "Chi df", "p")) %>%
            knitr::kable(caption = "Experiment 4 - Analysis of Factors - Collapsed", ) %>%
              kable_styling(full_width= F)
Exp4Anova2
save_kable(Exp4Anova2, "Experiment 4- Learning Performance - ANOVA Results - Collapsed.png")
```

#### Comparisons with EMMeans II

```{r Experiment 4 -  EM Means}
##Post-Hoc Effect of Condition
Exp4.Collapsed <- summarySE(data=Exp4Data,
                             measurevar = "RespCorr",
                             groupvars = "Collapse2")
Exp4.Collapsed.EM <- emmeans(afex.Exp4.2, ~Collapse2)
##Condition vs. Chance
Exp4.Collapsed.vchance <- test(Exp4.Collapsed.EM, adjust = "Tukey")
##Condition vs. Each Other
Exp4.Collapsed.vPairs <- data.frame(pairs(Exp4.Collapsed.EM, adjust = "Tukey" ))
###Category Baseline
Exp4.Collapsed.vPairs.1 <- 
  rbind(rep(NA,6),Exp4.Collapsed.vPairs[1:3,])
#Item Baseline
Exp4.Collapsed.vPairs.2 <- 
  rbind(Exp4.Collapsed.vPairs[1,], rep(NA,6),Exp4.Collapsed.vPairs[4:5,])
#Arbitrary Baseline
Exp4.Collapsed.vPairs.3 <- 
  rbind(Exp4.Collapsed.vPairs[2,], Exp4.Collapsed.vPairs[4,], rep(NA,6),Exp4.Collapsed.vPairs[6,])
#No Label Baseline
Exp4.Collapsed.vPairs.4 <- 
  rbind(Exp4.Collapsed.vPairs[3,],Exp4.Collapsed.vPairs[4,],Exp4.Collapsed.vPairs[6,], rep(NA,6))
###Creating a single dataframe for Blocks
Exp4.Collapsed.Combo <- cbind.data.frame (
  Exp4.Collapsed$Collapse2, Exp4.Collapsed$RespCorr, Exp4.Collapsed$sd,
  Exp4.Collapsed.vPairs.1$p.value,
  Exp4.Collapsed.vPairs.2$p.value,
  Exp4.Collapsed.vPairs.3$p.value,
  Exp4.Collapsed.vPairs.4$p.value
)
colnames(Exp4.Collapsed.Combo) <- c("Condition", "Mean", "SD", 
                                "Category Labels",
                                 "Item Labels (Systematic)",
                                 "Arbitrary Labels",
                                 "No Labels")
###Knitting Condition Table
Exp4PostHoc.Collapsed <- 
  Exp4.Collapsed.Combo %>%  
    mutate_if(is.numeric, round, 3) %>%
      mutate_at(.vars = vars("Category Labels", "Item Labels (Systematic)",
                             "Arbitrary Labels", "No Labels"),
      funs(ifelse(.<0.001, "<0.001", .))) %>%
      knitr::kable(caption = 'Experiment 4- Post Hoc Comparisons - Omnibus', "html") %>%
            kable_styling(full_width = F) %>%
              add_header_above(c("", "Descriptive Stats" = 2, 
                "Post-Hoc Comparisons to Other Conditions (p values)" = 4),
                   font_size = 12)
Exp4PostHoc.Collapsed
save_kable(Exp4PostHoc.Collapsed, "Experiment 4- Learning Performance - Omnibus Post Hoc Comparison.png")
```



